The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-13 r_r/tables_and_figures.Rmd
updates to manuscript

@@

@@

```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
```

```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
```

>>>>

```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs. visited private high schools in the South, public research universities"}
include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
```

```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs. visited private high schools in the South, selective private universities"}
include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
```

@@

```{r plot-2mode, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Two-mode network for private high schools and all visiting universities, colored by cluster"}
include_graphics(file.path(figures_dir, 'plot_2mode_all.pdf'))
```

@@

```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public research institutions, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
```

```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for selective private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
```

### 2023-12-13 r_r/tables_and_figures.tex
revising intro, adding revised tables
updates to manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newcommand{\beginsupplement}{
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

@@

@@

\caption{One-mode network for public institutions, colored by cluster}\label{fig:plot-1mode-pubu}
\end{figure}

@@

\caption{One-mode network for private universities, colored by cluster}\label{fig:plot-1mode-privu}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newcommand{\beginsupplement}{
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/race_comp_pubu_privhs_pubhs}

\caption{Racial composition of students at visited public high schools vs. visited private high schools in the South, public research universities}\label{fig:race-comp-pubu-privhs-pubhs}
\end{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/race_comp_privu_privhs_pubhs}

\caption{Racial composition of students at visited public high schools vs. visited private high schools in the South, selective private universities}\label{fig:race-comp-privu-privhs-pubhs}
\end{figure}

@@

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_2mode_all}

\caption{Two-mode network for private high schools and all visiting universities, colored by cluster}\label{fig:plot-2mode}
\end{figure}

@@

\caption{One-mode network for public research institutions, colored by cluster}\label{fig:plot-1mode-pubu}
\end{figure}

@@

\caption{One-mode network for selective private universities, colored by cluster}\label{fig:plot-1mode-privu}
\end{figure}
